Reporte - Análisis del Año

### 2019-12-13 manuscript.Rmd
update-manus

---
title: 'Reporte - Análisis del Año'
author: ""
output:
    html_document:
        smart: false
        toc: true
        toc_float: true
        number_sections: true

---

>>>>

---
title: 'Reporte - Análisis del Año'
author: ""
output:
    html_document:
        smart: false
        toc: true
        toc_float: true
        number_sections: true
bibliography: "refdocs/biblio.bib"
csl: "refdocs/apa6.csl"
---
